---
title: "N Parameters"
author: "Roshan Ranganathan"
format: html
execute: 
  echo: false
---

```{r}
library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)
```


```{r}
ch10_data <- shaming |>
mutate(p_00 = (primary_00 == "Yes"), p_02 = (primary_02 == "Yes"),
       p_04 = (primary_04 == "Yes"), g_00 = (general_00 == "Yes"),
       g_02 = (general_02 == "Yes"), g_04 = (general_04 == "Yes"),
civ_engage = p_00 + p_02 + p_04 + g_00 + g_02 + g_04,
voter_class = case_when(civ_engage %in% c(5, 6) ~ "Always Vote",
                        civ_engage %in% c(3, 4) ~ "Sometimes Vote",
                        civ_engage %in% c(1, 2) ~ "Rarely Vote"),
voter_class = factor(voter_class, levels = c("Rarely Vote", "Sometimes Vote", "Always Vote")), age_z = as.numeric(scale(age))) |>
  rename(voted = primary_06) |>
  select(voted, treatment, sex, age_z, civ_engage, voter_class) |>
  drop_na() |>
  slice_sample(prop = 0.1)
```

```{r}
ch10_data |> sample_frac(0.5) |> 
  ggplot(aes(x = civ_engage, y = voted)) +
    geom_jitter(alpha = 0.03, height = 0.1) +
    scale_x_continuous(breaks = 1:6) + 
    scale_y_continuous(breaks = c(0, 1), labels = c("No", "Yes")) +
    labs(title = "Civic Engagement and Voting Behavior in Michigan",
         subtitle = "Past voting predicts future voting.",
         x = "Civic Engagement",
         y = "Voted in 2006 Primary Election",
         caption = "Random sample of 5% of the data from Gerber, Green, and Larimer (2008)")
```

Using data from an experiment to determine if people are motivated to vote by social pressure, we seek to forecast the causal effect on voter participation by sending postcards in the Texas election of 2026. Our goal is to determine to what extent social pressure affects voters' decisions. One Quantity of Interest (QoI) is the difference in voter participation rates between those who received a postcard and those who did not. Our Bayesian regression model estimates this effect, but we must consider the uncertainty in our results due to changing political views and behaviors over time. Stability may not hold because viewpoints on politics have changed and will continue to change.
$$y_{i} = \beta_{0} + \beta_{1} age\_z + \beta_{2}male_i + \beta_{3}civic\_duty_i + \\ \beta_{4}hawthorne_i + \beta_{5}self_i + \beta_{6}neighbors_i + \\ \beta_{7}Sometimes\ vote_i + \beta_{8}Always\ vote_i + \\ \beta_{9}civic\_duty_i Sometimes\ vote_i + \beta_{10}hawthorne_i Sometimes\ vote_i + \\ \beta_{11}self_i Sometimes\ vote_i + \beta_{11}neighbors_i Sometimes\ vote_i + \\ \beta_{12}civic\_duty_i Always\ vote_i + \beta_{13}hawthorne_i Always\ vote_i + \\ \beta_{14}self_i Always\ vote_i + \beta_{15}neighbors_i Always\ vote_i + \epsilon_{i}$$

```{r}
#|label: model
#|cache: true

fit_postcard_vote <- brm(formula = voted ~ age_z + sex + treatment + voter_class + treatment*voter_class, 
data = ch10_data, 
family = gaussian(), 
refresh = 0, 
silent = 2, 
seed = 19)

```

```{r}
fit_postcard_vote |> 
  tbl_regression(intercept = TRUE, estimate_fun = function(x) style_sigfig(x, digits = 3))
```

```{r}
fit_postcard_vote |>
  add_epred_draws(newdata = ndata)
```

